Constraint Programming - Inside Gecode

### 2014-05-06 paper.tex
added introductionary part to the section on search algorithms

	In the following part I will discuss these searches and additional techniques, which can be applied during searches in constraint programming.

@@

	The Depth-first search is a good point to start, as it was also historical the first developed one. The idea behind this search algorithm is that every possible combination of variables is examined. Obviously in its basic form it can not be applied to problems with inifinite domains; for problems with such variable domains it is necessary to use for instance Branch-and-reduce. Sometimes the Depth-first search is also referred to as chronological backtrack search.

>>>>

	In the following part I will discuss branching strategies, the Depth-first search and one of its variants, the Branch-and-bound search, the Limited-Discrepancy search as candidate for an improved backjumping-strategy, backjumping strategies in general and restart strategies.

@@

	\subsubsection{Depth-First Search}
	The Depth-first search is a good point to start, as it was also historical the first developed one. The idea behind this search algorithm is that every possible combination of variables is examined. Obviously in its basic form it can not be applied to problems with inifinite domains; for problems with such variable domains it is necessary to use for instance Branch-and-reduce. Sometimes the Depth-first search is also referred to as chronological backtrack search.
